FinalManuscript_DISCS_UG

### 2018-07-15 parts/01_introduction_05scopeandlimitations.tex
Added image quality tests to ch3
Revisions to Ch1
Revised 2.3 and ch3

We will implement and test the following algorithms:
\begin{enumerate}
	\item A modified version of the Paillier cryptosystem \cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}.
	\item An elliptic curve and ElGamal based cryptosystem for homomorphic encryption presented by Li, et. al. \cite{li_elliptic_2012}.
	\item A fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}, which is an improvement on the original lattice-based cryptosystem presented by Gentry \cite{gentry_fully_2009}.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Image adjustment
	\item Operations based on convolution
	\item Morphological operations
\end{enumerate}
We will adopt the benchmark for evaluating the performance and security of image encryption schemes presented by Ahmed, et. al \cite{ahmed_benchmark_2016}. The presented benchmark reflects many tests used in other literature \cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
	\item Tests for preservation of image quality after encryption and decryption.
	\begin{enumerate}
		\item Mean Squared Error (MSE)
		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
		\item Noise tolerance
	\end{enumerate}
	\item Tests for cryptographic security
	\begin{enumerate}
		\item Information entropy analysis
		\item Correlation coefficient analysis
		\item Differential analysis (number of pixel change rate (NPCR), universeral average change intensity (UACI))
	\end{enumerate}
\end{enumerate}
A detailed overview of the above will be provided in the methodology.
Both greyscale and color images will be used in the study.

Our library for OpenCV will be implemented in the C++ programming language.

>>>>

We will implement and test the following algorithms:
\begin{enumerate}
	\item A modified version of the Paillier cryptosystem \cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}.
	\item A fully homomorphic encryption scheme developed by Dasgupta and Pal, which uses polynomial rings \cite{dasgupta_design_2016}.
	\item A fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}, which is an improvement on the original lattice-based cryptosystem presented by Gentry \cite{gentry_fully_2009}.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Image adjustment
	\item Spatial filters/morphological operations
\end{enumerate}
We will adopt the benchmark for evaluating the performance and security of image encryption schemes presented by Ahmed, et. al \cite{ahmed_benchmark_2016}. The presented benchmark reflects many tests used in other literature \cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
	\item Tests for preservation of image quality after encryption and decryption.
	\begin{enumerate}
		\item Mean Squared Error (MSE)
		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
	\end{enumerate}
	\item Tests for cryptographic security
	\begin{enumerate}
		\item Information entropy analysis
		\item Correlation coefficient analysis
		\item Differential analysis (number of pixel change rate (NPCR), universal average change intensity (UACI))
	\end{enumerate}
\end{enumerate}
A detailed overview of the above will be provided in the methodology.
Both greyscale and color images will be used in the study.

### 2018-07-15 parts/02_relatedliterature.tex
Revised 2.3 and ch3

However, a major limitation of \textit{CryptoImg} is that it does not seem to tackle the problem of security. Even though the authors have established that the Paillier cryptosystem itself cannot be broken \cite{ziad_cryptoimg:_2016}, we believe that a cryptanalysis of the encrypted images after they have been operated is necessary, since image operations may be considered additional information in a known plaintext attack.

Furthermore, Ziad, et al. only presented a visual comparison and evaluation to establish the quality of the recovered images. We believe that additional image quality benchmarks, such as those presented in \cite{ahmed_benchmark_2016, ahmad_efficiency_2012}, would allow for quantitative comparisons of image quality.
This study can be further improved by also considering the use of other homomorphic cryptosystems like the elliptic curve-based ElGamal cryptosystem by Li, et al. \cite{li_elliptic_2012} and a fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010}, which is a variant of Gentry's lattice-based cryptosystem which can be expressed using elementary number theory, without the use of lattices.

@@

In particular, we aim to address the shortcoming of \textit{CryptoImg} by developing a library to test various homomorphic encryption schemes with the help of the \textit{HElib} library to be able to implement fully homomorphic encryption schemes. This helps us determine the practicality of using homomorphic cryptosystems in image processing, especially when dealing with more complex image operations.

>>>>

However, a major limitation of \textit{CryptoImg} is that it does not consider image security. Even though the authors have established that the Paillier cryptosystem itself cannot be broken \cite{ziad_cryptoimg:_2016}, we believe that a cryptanalysis of the encrypted images after they have been operated is necessary, since image operations may be considered additional information in a known plaintext attack.

Furthermore, Ziad, et al. only presented a visual comparison and evaluation to establish the quality of the recovered images. We believe that additional image quality benchmarks, such as those presented in \cite{ahmed_benchmark_2016, ahmad_efficiency_2012}, would allow for quantitative comparisons of image quality.

This study can be further improved by also considering the use of fully homomorphic cryptosystems such as the one presented by Dasgupta and Pal \cite{dasgupta_design_2016}, and the fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010} and improved by Gentry and Halevi  \cite{hutchison_implementing_2011}. These fully homomorphic cryptosytems have yet to be implemented for image processing operations.

@@

In particular, we aim to address the shortcomings of \textit{CryptoImg} by developing a library to test various homomorphic encryption schemes with the help of the \textit{HElib} library to be able to implement fully homomorphic encryption schemes efficiently. This helps us determine the practicality of using homomorphic cryptosystems in image processing, especially when dealing with more complex image operations.

### 2018-07-15 parts/02_relatedliterature_02commonimageprocessingoperations.tex
Revised 2.3 and ch3

In the CrytoImg software library, of the intensity transformations above, only image negation was implemented under a homomorphic cryptosystem \cite{ziad_cryptoimg}. To implement these intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead. In our software library implementation, we aim to investigate the overhead required to approximate these functions.

@@

\begin{figure*}[!ht]
    \centering
    \includegraphics[width=\textwidth,\keepaspectratio]{Figures/SpatialFilter.png}
    \caption{(a) A sample image $R$. (b) A sample kernel $k$.}
    \label{fig:spatialfilter}
\end{figure*}
For example, using the image and kernel given in Figure \ref{fig:spatialfilter}, we can calculate the value in the third row and fourth column of the resulting image $R^\prime$ as follows:
\begin{align*}
	R^\prime(3,4) &= \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(3+s,4+t)}}\\
	&= (0.0625\times 200) + (0.1250\times 249) + (0.0625\times 255) +\\
	&(0.1250\times 143) + (0.2500\times 223) + (0.1250\times 255) +\\
	&(0.0625\times 196) + (0.1250\times 236) + (0.0625\times 255)\\
	&= 223.
\end{align*}
Since spatial filters take values from a contiguous region of pixels, this presents a difficulty in homomorphic cryptosytems: in order for spatial filters to be performed, the location of each pixel relative to neighboring pixels has to be preserved. This was performed in the implementation of spatial filters in the CryptoImg library \cite{ziad_cryptoimg}. We wish to implement spatial filters using a similar approach, and assess how preserving spatial correlation between pixels can impact the security of the encrypted image.

>>>>

In the CrytoImg software library, of the intensity transformations above, only image negation was implemented under a homomorphic cryptosystem \cite{ziad_cryptoimg:_2016}. To implement these intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead. In our software library implementation, we aim to investigate the overhead required to approximate these functions.

@@

\begin{figure*}[!ht]
    \centering
    \includegraphics[width=\textwidth,\keepaspectratio]{Figures/SpatialFilter.png}
    \caption{(a) A sample image $R$. (b) A sample kernel $k$.}
    \label{fig:spatialfilter}
\end{figure*}
For example, using the image and kernel given in Figure \ref{fig:spatialfilter}, we can calculate the value in the third row and fourth column of the resulting image $R^\prime$ as follows:
\begin{align*}
	R^\prime(3,4) &= \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(3+s,4+t)}}\\
	&= (0.0625\times 200) + (0.1250\times 249) + (0.0625\times 255) +\\
	&(0.1250\times 143) + (0.2500\times 223) + (0.1250\times 255) +\\
	&(0.0625\times 196) + (0.1250\times 236) + (0.0625\times 255)\\
	&= 223.
\end{align*}
Since spatial filters take values from a contiguous region of pixels, this presents a difficulty in homomorphic cryptosytems: in order for spatial filters to be performed, the location of each pixel relative to neighboring pixels has to be preserved. This was performed in the implementation of spatial filters in the CryptoImg library \cite{ziad_cryptoimg:_2016}. We wish to implement spatial filters using a similar approach, and assess how preserving spatial correlation between pixels can impact the security of the encrypted image.

### 2018-07-15 parts/03_methodology.tex
Revised 2.3 and ch3

The study consists of two parts: first, the implementation of the three homomorphic encryption schemes and image processing operations under each scheme as an OpenCV library. The second part of the study consists of assessing the robustness and security of image operations under each encryption scheme using benchmarks in \cite{ahmed_benchmark_2016}.

@@

Three homomorphic encryption schemes will be implemented, those presented by Ziad, et al. \cite{ziad_cryptoimg:_2016}, Li, et al. \cite{li_elliptic_2012} and Smart and Vercauteren \cite{hutchison_fully_2010}. The encryption and decryption methods will be implemented in C++.

@@

\subsection{Evaluating Image Quality}
The benchmarks to be used in the study, adopted from \cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011} are listed below. We let $X_i$ denote a value in an image $X$, where $1 \leq i \leq N$.
We first perform three tests to ascertain the preservation of image quality after encryption and decryption: MSE, PSNR, and SSIM.
\begin{description}
	\item [Mean Squared Error (MSE).] The MSE is defined in \cite{ahmed_benchmark_2016} as
	\begin{align}
        \mathrm{MSE} = \frac{1}{N}\sum_{i=1}^{N}{(\mathrm{CDT}_i - \mathrm{PDT}_i)^2}.
	\end{align}
	The MSE provides a measure of how much data is recovered if an image operation is applied on the encrypted image, which is then decrypted. Lower values of MSE indicate higher preservation of image quality \cite{ahmed_benchmark_2016, ahmad_efficiency_2012}.
	\item [Peak Signal to Noise Ratio (PSNR).]
	According to Ahmed, et al. \cite{ahmed_benchmark_2016}, PSNR is ``an estimator for human visual perception of reconstruction quality'' which is based on  It has been used to ascertain image quality in various studies and is a known meetric for image and video quality \cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}. Although it may produce results which do not correlate with human visual perception \cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared \cite{huynh-thu_accuracy_2012}.
	PSNR is defined by
	\begin{align}
        \mathrm{PSNR} = 10\log_{10}{\left( \frac{L^2}{\mathrm{MSE}} \right)}
	\end{align}
	where $L$ is the maximum pixel intensity value of an image.
	Despite the known limitations of PSNR, since we are going to compare the effect of each encryption scheme on recovered image quality, given a fixed library of images, it is a valid measure of image quality for the study. A higher PSNR indicates higher image quality preservation.
	\item [Structural Similarity Index (SSIM).]
	The SSIM for two random variables $X$ and $Y$ is defined in \cite{ahmed_benchmark_2016, akramullah_video_2014} as
	\begin{align}
        \mathrm{SSIM}(X,Y) = \frac{(2\mu_X\mu_Y+c_1)(2\sigma_{XY}+c_2)}{(\mu_X^2+\mu_Y^2+c_1)(\mu_X^2+\mu_Y^2+c_2)}
	\end{align}
	where
	\begin{itemize}
		\item $\mu_X, \mu_Y$ are the averages of $X$ and $Y$, respectively;
		\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
		\item $\sigma_{XY}$ is the covariance of $X$ and $Y$;
		\item $c_1 = (k_1L)^2, c_2 = (k_2L)^2$ are two variables used to stabilize the measure when $\mu_X^2+\mu_Y^2$ is close to zero \cite{akramullah_video_2014};
		\item $L$ is the the maximum pixel intensity value of an image;
		\item $k_1 = 0.01, k_2 = 0.03$ by default, given in \cite{ahmed_benchmark_2016}.
	\end{itemize}
	The SSIM is applied to the luminance value of two images to gauge structural similarity between neighboring pixels.
    For the study, we will compute $\mathrm{SSIM}(\mathrm{PDT}, \mathrm{CDT})$ for every image operation, under each homomorphic cryptosystem. Higher values of SSIM indicate higher structural similarity, and an SSIM of 1 indicates that the two images are identical\cite{ahmed_benchmark_2016}.
\end{description}

@@

In summary, the study will consist of
\begin{itemize}
	\item An implementation of an OpenCV library which implements homomorphic cryptosystems by Ziad, et al. \cite{ziad_cryptoimg:_2016}, Li, et al. \cite{li_elliptic_2012} and Smart and Vercauteren \cite{hutchison_fully_2010}.
	\item An implementation of image processing operations (intensity transformations, spatial filters) under the above cryptosystems.
	\item Conducting tests for image quality, processing time, and cryptographic security, using standard test images from \cite{gonzalez_image_nodate}.
\end{itemize}

>>>>

The study consists of two parts: first, the implementation of the three homomorphic encryption schemes \cite{ziad_cryptoimg:_2016, dasgupta_design_2016, hutchison_fully_2010} and image processing operations under each scheme as an OpenCV library. While the scheme in \cite{ziad_cryptoimg:_2016} has been implemented for use in image processing, the fully homomorphic systems \cite{dasgupta_design_2016, hutchison_fully_2010} will have to be adapted for image processing. in The second part of the study consists of assessing the robustness and security of image operations under each encryption scheme using benchmarks in \cite{ahmed_benchmark_2016}.

@@

Three homomorphic encryption schemes will be implemented, those presented by Ziad, et al. \cite{ziad_cryptoimg:_2016}, Dasgupta and Pal \cite{dasgupta_design_2016} and Smart and Vercauteren \cite{hutchison_fully_2010}. The encryption and decryption methods will be implemented in C++.

@@

\subsection{Evaluating Image Quality}
The benchmarks to be used in the study, adopted from \cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011} are listed below. We let $X_i$ denote a value in an image $X$, where $1 \leq i \leq N$.
We first perform three tests to ascertain the preservation of image quality after encryption and decryption: MSE, PSNR, and SSIM.
\begin{description}
	\item [Mean Squared Error (MSE).] The MSE is defined in \cite{ahmed_benchmark_2016} as
	\begin{align}
        \mathrm{MSE} = \frac{1}{N}\sum_{i=1}^{N}{(\mathrm{CDT}_i - \mathrm{PDT}_i)^2}.
	\end{align}
	The MSE provides a measure of how much data is recovered if an image operation is applied on the encrypted image, which is then decrypted. Lower values of MSE indicate higher preservation of image quality \cite{ahmed_benchmark_2016, ahmad_efficiency_2012}.
	\item [Peak Signal to Noise Ratio (PSNR).]
	According to Ahmed, et al. \cite{ahmed_benchmark_2016}, PSNR is ``an estimator for human visual perception of reconstruction quality''. It has been used to ascertain image quality in various studies and is a known metric for image and video quality \cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}. Although it may produce results which do not correlate with human visual perception \cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared \cite{huynh-thu_accuracy_2012}.
	PSNR is defined by
	\begin{align}
        \mathrm{PSNR} = 10\log_{10}{\left( \frac{L^2}{\mathrm{MSE}} \right)}
	\end{align}
	where $L$ is the maximum pixel intensity value of an image.
	Despite the known limitations of PSNR, since we are going to compare the effect of each encryption scheme on recovered image quality, given a fixed library of images, it is a valid measure of image quality for the study. A higher PSNR indicates higher image quality preservation.
	\item [Structural Similarity Index (SSIM).]
	The SSIM for two random variables $X$ and $Y$ is defined in \cite{ahmed_benchmark_2016, akramullah_video_2014} as
	\begin{align}
        \mathrm{SSIM}(X,Y) = \frac{(2\mu_X\mu_Y+c_1)(2\sigma_{XY}+c_2)}{(\mu_X^2+\mu_Y^2+c_1)(\mu_X^2+\mu_Y^2+c_2)}
	\end{align}
	where
	\begin{itemize}
		\item $\mu_X, \mu_Y$ are the averages of $X$ and $Y$, respectively;
		\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
		\item $\sigma_{XY}$ is the covariance of $X$ and $Y$;
		\item $c_1 = (k_1L)^2, c_2 = (k_2L)^2$ are two variables used to stabilize the measure when $\mu_X^2+\mu_Y^2$ is close to zero \cite{akramullah_video_2014};
		\item $L$ is the the maximum pixel intensity value of an image;
		\item $k_1 = 0.01, k_2 = 0.03$ by default, given in \cite{ahmed_benchmark_2016}.
	\end{itemize}
	The SSIM is applied to the luminance value of two images to gauge structural similarity between neighboring pixels.
    For the study, we will compute $\mathrm{SSIM}(\mathrm{PDT}, \mathrm{CDT})$ for every image operation, under each homomorphic cryptosystem. Higher values of SSIM indicate higher structural similarity, and an SSIM of 1 indicates that the two images are identical\cite{ahmed_benchmark_2016}.
\end{description}

@@

In summary, the study will consist of
\begin{itemize}
	\item An implementation of an OpenCV library which implements homomorphic cryptosystems by Ziad, et al. \cite{ziad_cryptoimg:_2016}, Dasgupta and Pal \cite{dasgupta_design_2016} and Smart and Vercauteren \cite{hutchison_fully_2010}.
	\item An implementation of image processing operations (intensity transformations, spatial filters) under the above cryptosystems.
	\item Conducting tests for image quality, processing time, and cryptographic security, using standard test images from \cite{gonzalez_image_nodate}.
\end{itemize}
